---
title: "Introduction to binomial"
author: "Adele Shen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Creating an object of class `"binvar"` with the `bin_variable` function

This returns a list of the parameters you have set for your binomial variable.

```{r}
bvar = bin_variable(trials = 10, prob = 0.3)
```
Using the `"binvar"` object, you can then use `print.summary.binvar()` to see more characteristics of the binomial variable you just defined, such as measurements like mean, variance, etc.

```{r, eval = FALSE}
print.summary.binvar(bvar)
```

## Binomial Measures

You can make different calculations / measurements of a binomial random variable specified first by the number of trials and secondly by the probability of success.

```{r, eval = FALSE}
bin_mean(trials = 10, prob = 0.3)

bin_variance(10, 0.3)

bin_mode(10, 0.3)

bin_skewness(10, 0.3)

bin_kurtosis(10, 0.3)

```

## The Binomial Distribution

Preliminarily, you can calculate the total number of combinations of choosing k items or events from a total n with `bin_choose()`

```{r, eval = FALSE}
bin_choose(n = 5, k = 2)
```

To calculate the probability of getting a certain number of successes in a certain number of identically distributed and independent trials with a fixed probablility of success, just use `bin_probability()`.

```{r, eval = FALSE}
bin_probability(trials = 5, prob = 0.5)
```

If you want the entire probability distribution (in a data.frame of class `"bindis"` and `"data.frame"`), use `bin_distribution()`. For the binomial cumulative distribution, use `bin_cumulative()`, which will return a data.frame of class `"bincum"` and `"data.frame"`. You can also plot these with `plot.bindis()` and `plot.bincum()` respectively, which respectively return a probability histogram and a line graph that asymptotically approaches 1 on the right.

```{r, eval = FALSE}
distr = bin_distribution(trials = 5, prob = 0.5)
plot.bindis(distr)

cdist = bin_cumulative(trials = 5, prob = 0.5)
plot.bincum(cdist)
```














