---
title: "lab05-adele-shen"
output: html_document
---
## 1) Lab Directory
```{r eval = FALSE}
pwd
/Users/AdeleShen

cd Desktop/STAT133/labs/lab05

pwd 
/Users/AdeleShen/Desktop/STAT133/labs/lab05

mkdir stat133-lab05
cd stat133-lab05

curl -O http://textfiles.com/food/bread.txt

ls
bread.txt	stat133-lab05

curl -O http://textfiles.com/food/btaco.txt
curl -O http://textfiles.com/food/1st_aid.txt
curl -O http://textfiles.com/food/beesherb.txt
curl -O http://textfiles.com/food/bakebred.txt
curl -O http://archive.ics.uci.edu/ml/machine-learning-databases/forest-fires/forestfires.csv
curl -O http://web.pdx.edu/~gerbing/data/cars.csv
curl -O http://web.pdx.edu/~gerbing/data/color.csv
curl -O http://web.pdx.edu/~gerbing/data/snow.csv
curl -O http://web.pdx.edu/~gerbing/data/mid1.csv
curl -O http://web.pdx.edu/~gerbing/data/mid2.csv
curl -O http://web.pdx.edu/~gerbing/data/minutes1.csv
curl -O http://web.pdx.edu/~gerbing/data/minutes2.csv
```

## 2) Inspecting a Directory 
```{r eval = FALSE}
ls

ls -l

man ls
ls -l -r

ls *.txt

ls -r *.csv
snow.csv	minutes1.csv	mid1.csv	color.csv
minutes2.csv	mid2.csv	forestfires.csv	cars.csv

ls ????.csv
cars.csv	mid1.csv	mid2.csv	snow.csv

ls *[1]*.csv
mid1.csv	minutes1.csv

ls *[2]*.csv
mid2.csv	minutes2.csv

ls *[[:digit:]*]*
1st_aid.txt	mid1.csv	mid2.csv	minutes1.csv	minutes2.csv

ls *[0-9]*.csv
```

## 3) Moving Files
```{r eval = FALSE}
cd data
mkdir txt-files
mkdir csv-files
man mv
mv ../bread.txt ./txt-files/
  
ls ./txt-files
bread.txt

mv ../*txt ./txt-files
ls ./txt-files

mv ../*csv ./csv-files
ls ./csv-files

tree 
```

## 4) Copying Files
```{r eval = FALSE}
cd ..
mkdir copies
cp data/txt-files/bread.txt copies/
  
ls copies
bread.txt

cp data/txt-files/* copies/
ls copies

cp data/csv-files/* copies/
  
tree
```

## 5) Renaming and Deleting Files

```{r eval = FALSE}
cd copies
mv bread.txt bread-recipe.txt
mv btaco.txt breakfast-taco.txt

cd ..
mv copies copy-files

rm copy-files/*csv
rm -r copy-files

ls -r data/txt-files
```

pwd: print working directory
ls: list files and directories
cd: change directory (move to another directory)
mkdir: create a new directory
touch: create a new (empty) file
cp: copy file(s)
mv: rename file(s)
rm: delete file(s)

# Lab Part 2
## Abalone
```{r eval = FALSE}
mkdir abalone
cd abalone
curl -O http://archive.ics.uci.edu/ml/machine-learning-databases/abalone/abalone.data

file abalone.data
abalone.data: ASCII text

wc abalone.data
    4177    4177  191873 abalone.data (line word byte)
    
wc -l abalone.data
head abalone.data
head -5 abalone.data
head -15 abalone.data

tail abalone.data
tail -3 abalone.data

less abalone.data

mv abalone.data abalone.csv

cp abalone.csv dataset.csv
mv dataset.csv ../data/csv-files/
```

## Exporting Objects from R to External Files
```{r eval = FALSE}
cd ..
mkdir exports
```

```{r}
head(mtcars)
getwd()
```

```{r}
write.csv(
  x = mtcars, # R object to be exported
  file = 'stat133-lab05/exports.csv'  # file path
)
```

```{r}
sink(file = 'stat133-lab05/summary-mpg-disp.txt')
summary(mtcars[ ,c('mpg', 'disp')])
# closing sinking operation
sink()
```

```{r, message= FALSE, warning=FALSE}
png(filename = "stat133-lab05/exports/scatterplot-mpg-disp.png")
plot(mtcars$mpg, mtcars$disp, pch = 20, 
     xlab = 'Miles per Gallon', ylab = 'Displacement')
dev.off()
```

```{r}
# Export a data frame with columns mpg, disp, and hp, to a CSV file dataset.csv in the exports/ subdirectory.
write.csv(
  x = select(mtcars, mpg, disp, hp), # R object to be exported
  file = 'stat133-lab05/exports/datasets.csv'  # file path
)
```

```{r}
# Export the output of str() on mtcars to a text file called mtcars-structure.txt (inside the exports/ subdirectory).
sink(file = 'stat133-lab05/exports/mtcars-structure.txt')
str(mtcars)
# closing sinking operation
sink()
```


```{r}
# Export the summary() of the entire data frame mtcars to a text file summary-mtcars.txt, in the exports/ folder.
sink(file = 'stat133-lab05/exports/summary-mtcars.txt')
summary(mtcars)
# closing sinking operation
sink()
```

```{r}
# Use png() to save a scatterplot of mpg and wt with plot(). Save the graph as scatterplot-mpg-wt.png in the exports/ folder.

png(filename = "stat133-lab05/exports/scatterplot-mpg-wt.png")
plot(mtcars$mpg, mtcars$wt, pch = 20)
dev.off()
```

```{r}
#Save another version of the scatterplot between hp and wt, but now try to get an image with higher resolution. Save the plot as scatterplot-hp-wt.png in exports/
png("stat133-lab05/exports/scatterplot-hp-wt.png")
plot(mtcars$mpg, mtcars$wt, pch = 20, res = 150)
dev.off()
```
```{r}
# Save a histogram in JPEG format of mpg with dimensions (width x height) 600 x 400 pixels, name the file histogram-mpg.jpeg
jpeg("stat133-lab05/exports/histogram-mpg.jpeg", width = 600, height = 400)
ggplot(mtcars) + geom_histogram(aes(mtcars$mpg), binwidth = 1.5)
dev.off()
```

```{r}
# Use pdf() to save the previous histogram of age in PDF format, with dimensions (width x height) 7 x 5 inches, name the file histogram-mpg.pdf.
pdf("stat133-lab05/exports/histogram-mpg.pdf", width = 7, height = 5)
hist(mtcars$mpg)
dev.off()
```

```{r}
# Use ggplot() to make a scatterplot of mpg and disp, and store it in a ggplot object named gg_mpg_disp. Then use ggsave() to save the plot with dimensions (width x height) 7 x 5 inches, as scatterplot-mpg-disp.pdf

ggsave("stat133-lab05/exports/scatterplot-mpg-disp.pdf", width = 7, height = 5)
gg_mpg_disp = ggplot(mtcars) +
  geom_point(aes(x = mtcars$mpg, y = mtcars$disp))
```



